	% Meeting 1
	\section*{Sept. 11, 2025}
	\addcontentsline{toc}{section}{Meeting 1}

	\textbf{Attendees:} Abdul, Tabish, Berk, Andrew (online) \\
	\textbf{Notetaker:} Nicholas

		\subsection*{Agenda:}
			\subsubsection*{Team Technology}
			\begin{itemize}
				\item Messaging/Communication: Teams 
				\item Files- onedrive/sharepoint, eventually all Github (especially source files)
				\item CI/CD- optional since we’re tron, should do some CI as is convenient and helps us, should be fire and forget
				\item Berk makes the repo
				\item Refining scope given by Andrew into an email to Dr. Wassyng for approval for Berk’s entry into the group. Will then slightly rotate it into the group formation message required for the deliverable.
				\item Regular meeting during tutorial time (first hour), in person
				\item Andrew as Liasion, chair
				\item Nicholas as scribe
				\item Python for now, cython exists if speedup needed
				\item Can split computation into recording data/hardware interface, processing is separate task on another computer. Want to start over on that code, could pick fresh start. Various C/C++ libraries for these tasks
				\item Possible stretch goal to have a backend, database to back up info/sync btn pi and server
				\item Probably have a linter, Berk will see to it. Can follow formal convention, put issue number in commit message: https://www.conventionalcommits.org/en/v1.0.0/
			\end{itemize}
		\subsection*{Future Work}
			\begin{itemize}
				\item Explore existing literature (aka the code from the last group, or Andrew's from last year)
				\item Figure out how the power delivery board works, determine whether we can reuse 
				\item Sent out GitHub IDs to Andrew to share the code with us
			\end{itemize}
		\subsection*{Deliverables}
			\begin{itemize}
				\item Next deliverable is September 21st, 10 days from now; form teams, project description. 
				\item Berk has emailed the professors about his case, will move towards the team formation deliverable based on that. 
			\end{itemize}	
